He-Man: A domain-specific language for lightweight concurrency

### 2011-12-13 report/report.tex
Future work.

For our experiments, the server ran Linux kernel 3.0.0 on a Lenovo
Thinkpad W520 with a quad core 2.3 GHz Intel Core i7-2820QM and 8
gigabytes of RAM, and the client ran on a Lenovo Thinkpad T500 with a
Intel Core 2 Duo and 8 gigabtyes of RAM.  % XXX: client specs
The machines were connected by a gigabit Ethernet link.

@@

say something about Memory.hs??

@@

multithreaded runtime

write a better allocator

less space per thread

decide when to allow internal if statements

We will additionally output a graphical representation of this underlying state
machine.

observable sharing (?)

>>>>

For our experiments, the server ran Linux kernel 3.0.0 on a Lenovo
Thinkpad W520 with a quad core 2.3 GHz Intel Core i7-2820QM and 8
gigabytes of RAM, and the client ran on a Lenovo Thinkpad T500 with a
Intel Core 2 Duo and 8 gigabytes of RAM.  % XXX: client specs
The machines were connected by a gigabit Ethernet link.

@@

% see how many threads we can spawn with Memory.hs

@@

We will continue our work on He-Man, and hope to submit it to a programming
languages conference such as ICFP. We plan to expand the language with the
ability to declare functions and make non-external function calls within a
thread. This will make code simpler and shorter by allowing the programmer to
abstract away common functionality like read and write loops.

In the runtime, our current thread \t{struct}s are larger than necessary.
Because the runtime allocates a \t{struct} on every thread spawn, we should
replace our \t{malloc} calls with calls to a custom slab allocator. We also plan
on writing a multithreaded runtime, to allow servicing multiple threads' ready
events simultaneously. Because our threads don't interact, this does not require
exposing any locking to the programmer.

The backend can perform more aggressive optimization on the code blocks. In
particular, we currently do not allow any control flow except at tail position;
if both branches of an \t{if} are non-blocking, we should avoid translating it
into multiple blocks, requiring a yield to the main loop. It should also be
possible to gather interesting output from the backend, like a graphical
representation of the generated state machine, for documentation purposes.

We also hope to implement observable sharing, as in \cite{Gill}, to allow the
same thread to have distinct spawn sites without code duplication. This does not
add inefficiency, but does increase the size of our output code.
